---
title: "Variable relevance measures (GAM model)"
subtitle: "House renting prices from Idealista.com (new)"
author: "Pedro Delicado, Daniel Peña"
date: "27th January 2020"
output:
  html_document:
    df_print: paged
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data from Idealista.com 


The data come from [idealista-data] (https://github.com/seralexger/idealista-data)

Author: Alejandro German (Alex seralexger)

(Douwnloaded March 2nd, 2018)

The R-markdown file `rent_housing_data.Rmd" has been used to read the data and to save some of them into `"rhBM_Price.Rdata"`.

```{r}
load(file="rhBM_Price.Rdata") 
# rhBM.price, rhBM.priceByArea,
names(rhBM.price)
log.size <- TRUE
if (log.size){
  rhBM.price$size <- log(rhBM.price$size)
  names(rhBM.price)[11]<-"log.size"
} 
```

```{r}
names(rhBM.priceByArea)
```

We define training and test set, fit these models, and apply variable relevance measures.

### Training and test sets

```{r}
n <- dim(rhBM.price)[1]
pr.tr <- .7
pr.te <- 1 - pr.tr
n.tr <- round(n*pr.tr)
set.seed(123456)
Itr <- sample(1:n,n.tr)
Ite <- setdiff(1:n,Itr)
n.te <- n.tr 
```

### Additive model for log(price)

```{r}
library(mgcv)

if (log.size){
  ad.mod.form <- "log(price) ~ Barcelona + 
s(categ.distr,k=3) + 
type.chalet + type.duplex + type.penthouse + type.studio + 
s(floor) + hasLift + 
s(floorLift,k=6) + 
s(log.size) + exterior + 
s(rooms) + s(bathrooms,k=6) + 
hasParkingSpace + ParkingInPrice + 
s(log_activation)"
}else{
  ad.mod.form <- "log(price) ~ Barcelona + 
s(categ.distr,k=3) + 
type.chalet + type.duplex + type.penthouse + type.studio + 
s(floor) + hasLift + 
s(floorLift,k=6) + 
s(size) + exterior + 
s(rooms) + s(bathrooms,k=6) + 
hasParkingSpace + ParkingInPrice + 
s(log_activation)"
}

am.logprice <- gam(as.formula(ad.mod.form), data=rhBM.price[Itr,])
1-(mean(am.logprice$residuals^2)/var(log(rhBM.price$price)))
#[1] 0.7803967
(sum.am.logprice <- summary(am.logprice))
``` 

```{r}
plot(log(rhBM.price$price[Itr]),am.logprice$fitted.values,
     main=paste("Corr^2=",round(cor(log(rhBM.price$price[Itr]),am.logprice$fitted.values)^2,2)))
```

```{r, fig.height=10, fig.width=10}
plot(am.logprice, residuals = TRUE, pages=1)
```


```{r}
# Predicting in the test sample
y.hat.te <- as.numeric( predict(am.logprice, newdata = rhBM.price[Ite,]) )

plot(log(rhBM.price$price[Ite]),y.hat.te,
     main=paste("Corr^2=",round(cor(log(rhBM.price$price[Ite]),y.hat.te)^2,2)))

```

### Variable relevance measures

```{r}
library(mgcv)
library(ggplot2)
library(grid)
library(maptools)# For pointLabel

source("R_scripts/relev.ghost.var.R")
source("R_scripts/relev.rand.perm.R")
```

## Variable relevance matrix by ghost variables

```{r, fig.height=14, fig.width=14}
relev.ghost.out <- relev.ghost.var(model=am.logprice, 
                             newdata = rhBM.price[Ite,],
                             func.model.ghost.var= lm)
```


```{r final.graf.Gh, fig.height=14, fig.width=14}
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, resid.var=am.logprice$sig2,
                                 vars=1:7, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
```

```{r final.graf.Gh.pdf, eval=FALSE}
pdf(file="newVarRlevIdealista_gam_Gh.pdf", height=16, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, resid.var=am.logprice$sig2,
                                 vars=1:7, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
dev.off()
```

## Variable relevance matrix by random permutation

```{r}
relev.rand.out <- relev.rand.perm(model=am.logprice, 
                              newdata = rhBM.price[Ite,])
```

```{r, fig.height=14, fig.width=14}
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:7, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
```

```{r final.graf.RP.pdf, eval=FALSE}
pdf(file="newVarRlevIdealista_gam_RP.pdf", height=16, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:7, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
dev.off()
```