---
title: "Variable relevance measures (linera model)"
subtitle: "House renting prices from Idealista.com (new)"
author: "Pedro Delicado, Daniel Pe?a"
date: "14th July 2019"
output:
  html_document:
    df_print: paged
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data from Idealista.com 


The data come from [idealista-data] (https://github.com/seralexger/idealista-data)

Author: Alejandro German (Alex seralexger)

(Douwnloaded March 2nd, 2018)

The R-markdown file `rent_housing_data.Rmd" has been used to read the data and to save some of them into `"rhBM_Price.Rdata"`.

```{r}
load(file="rhBM_Price.Rdata") 
# rhBM.price, rhBM.priceByArea,
names(rhBM.price)
log.price <- TRUE
if (log.price){
  rhBM.price$price <- log(rhBM.price$price)
  names(rhBM.price)[1]<-"log.price"
} 
log.size <- TRUE
if (log.size){
  rhBM.price$size <- log(rhBM.price$size)
  names(rhBM.price)[11]<-"log.size"
} 
```

```{r}
names(rhBM.priceByArea)
```

We define training and test set, fit these models, and apply variable relevance measures.

### Training and test sets

```{r}
n <- dim(rhBM.price)[1]
pr.tr <- .7
pr.te <- 1 - pr.tr
n.tr <- round(n*pr.tr)
set.seed(123456)
Itr <- sample(1:n,n.tr)
Ite <- setdiff(1:n,Itr)
n.te <- n-n.tr 
```

### Linear model

```{r}
# lm.logprice
lm.logprice <- lm(log.price~., data=rhBM.price[Itr,])
1-(mean(lm.logprice$residuals^2)/var(rhBM.price$log.price))
# [1] 0.7590134
(sum.lm.logprice <- summary(lm.logprice))

``` 
```{r}
cor(rhBM.price$log.price[Itr],lm.logprice$fitted.values)^2
# [1] 0.7620808
plot(rhBM.price$log.price[Itr],lm.logprice$fitted.values,
     main=paste("Corr^2=",round(cor(rhBM.price$log.price[Itr],lm.logprice$fitted.values)^2,2)))

plot(lm.logprice)
```


```{r}
# Predicting in the test sample
y.hat.te <- as.numeric( predict(lm.logprice, newdata = rhBM.price[Ite,]) )
cor(rhBM.price$log.price[Ite],y.hat.te)^2
# [1] 0.7665301
plot(rhBM.price$log.price[Ite],y.hat.te,
     main=paste("Corr^2=",round(cor(rhBM.price$log.price[Ite],y.hat.te)^2,2)))

```

### Variable relevance measures

```{r}
library(mgcv)
library(ggplot2)
library(grid)
library(maptools)# For pointLabel

source("../../R_scripts/relev.ghost.var.R")
source("../../R_scripts/relev.rand.perm.R")
```

## Variable relevance matrix by ghost variables

```{r, fig.height=14, fig.width=14}
relev.ghost.out <- relev.ghost.var(model=lm.logprice, newdata = rhBM.price[Ite,],                            func.model.ghost.var= lm)
```


```{r final.graf.Gh, fig.height=14, fig.width=14}
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.ghost.var(relev.ghost.out, n1=n.tr,
                     #resid.var=sum.lm.logprice$sigma^2,
                     vars=1:7, sum.lm.tr=sum.lm.logprice,
                     alpha=.01, ncols.plot=4)
```

```{r final.graf.Gh.pdf, eval=FALSE}
pdf(file="newVarRlevIdealista_Gh.pdf", height=16, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.ghost.var(relev.ghost.out, n1=n.tr,
                     # resid.var=sum.lm.logprice$sigma^2,
                     vars=1:7, sum.lm.tr=sum.lm.logprice,
                     alpha=.01, ncols.plot=3)
dev.off()
```

```{r final.graf.Gh.pdf.slides, eval=FALSE}
pdf(file="newVarRlevIdealista_Gh_2_4.pdf", height=12, width=16)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.ghost.var(relev.ghost.out, n1=n.tr,
                     # resid.var=sum.lm.logprice$sigma^2,
                     vars=1:7, sum.lm.tr=sum.lm.logprice,
                     alpha=.01, ncols.plot=4)
dev.off()
```
## Variable relevance matrix by random permutation

```{r}
relev.rand.out <- relev.rand.perm(model=lm.logprice, 
                              newdata = rhBM.price[Ite,])
```

```{r final.graf.rp, fig.height=14, fig.width=14}
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out,
                     relev.ghost=relev.ghost.out$relev.ghost,
                     vars=1:7, sum.lm.tr=sum.lm.logprice,
                     alpha=.01, ncols.plot=4)
```


```{r final.graf.RP.pdf, eval=FALSE}
pdf(file="newVarRlevIdealista_RP.pdf", height=12, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:6, sum.lm.tr=sum.lm.logprice,
                                 alpha=.01, ncols.plot=3)
dev.off()
```
```{r final.graf.RP.pdf.slides, eval=FALSE}
pdf(file="newVarRlevIdealista_RP_2_4.pdf", height=12, width=16)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:6, sum.lm.tr=sum.lm.logprice,
                                 alpha=.01, ncols.plot=4)
dev.off()
```
