---
title: "Variable relevance measures (Neural Network)"
subtitle: "House renting prices from Idealista.com (addendum after having sent the paper to publish)"
author: "Pedro Delicado, Daniel Peña"
date: "27th January 2020"
output:
  html_document:
    df_print: paged
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
printing <- FALSE
```

### Data from Idealista.com 


The data come from [idealista-data] (https://github.com/seralexger/idealista-data)

Author: Alejandro German (Alex seralexger)

(Douwnloaded March 2nd, 2018)

The R-markdown file `rent_housing_data.Rmd" has been used to read the data and to save some of them into `"rhBM_Price.Rdata"`.

```{r}
load(file="rhBM_Price.Rdata") 
# rhBM.price, rhBM.priceByArea,
names(rhBM.price)
log.price <- TRUE
if (log.price){
  rhBM.price$price <- log(rhBM.price$price)
  names(rhBM.price)[1]<-"log.price"
} 
log.size <- TRUE
if (log.size){
  rhBM.price$size <- log(rhBM.price$size)
  names(rhBM.price)[11]<-"log.size"
} 
```

```{r}
names(rhBM.priceByArea)
if (log.size){
  rhBM.priceByArea$size <- log(rhBM.priceByArea$size)
  names(rhBM.priceByArea)[11]<-"log.size"
} 
```

We define training and test set, fit these models, and apply variable relevance measures.

### Training and test sets

```{r}
n <- dim(rhBM.price)[1]
pr.tr <- .7
pr.te <- 1 - pr.tr
n.tr <- round(n*pr.tr)
set.seed(123456)
Itr <- sample(1:n,n.tr)
Ite <- setdiff(1:n,Itr)
n.te <- n.tr 
```

### Neural network log(price)

```{r, results='hide'}
require(nnet)

# centering and rescaling the explanatory variables before fitting the Neural Network
scaled.rhBM.price.tr <- as.data.frame(scale(as.matrix(rhBM.price[Itr,])))
scaled.rhBM.price.tr$price <- rhBM.price$price[Itr]
scaled.rhBM.price.te <- as.data.frame(scale(as.matrix(rhBM.price[Ite,])))
scaled.rhBM.price.te$price <- rhBM.price$price[Ite]
``` 

```{r, results='hide'}
# #set.seed(123)
# set.seed(1234)
# nnet.logprice <- nnet(log(price)~., data=scaled.rhBM.price.tr, 
#                size=10, linout=TRUE, maxit=100)
# 
# 1-(mean(nnet.logprice$residuals^2)/var(log(scaled.rhBM.price.tr$price)))
# # [1] 0.7779355 # with set.seed(1234),  size=10, linout=TRUE, maxit=100
# # [1] 0.7800399 # with set.seed(1234),  size=20, linout=TRUE, maxit=100
# # [1] 0.7930953 # with set.seed(1234),  size=20, linout=TRUE, maxit=200
# # [1] 0.7629634 # with set.seed(123),   size=10, linout=TRUE, maxit=100
# # [1] 0.7754375 # with set.seed(123),   size=20, linout=TRUE, maxit=100
# # [1] 0.7921368 # with set.seed(123),   size=20, linout=TRUE, maxit=200

first.time <- FALSE

if (first.time){
# tuning parameters "size" and "decay" using caret
require(caret)
ctrl <- trainControl(
  # method = "repeatedcv", # k-fold CV, k=num, repeated repeats times
  # repeats = 3, # number of repetitions of the k-fold CV
  method = "cv", # k-fold CV, k=num
  num=10 # default
)
nnetGrid = expand.grid(size = c(10,15,20), decay = c(0,.1,.3,.5))
set.seed(123)
nnetFit <- train(
  log.price~., 
  data=scaled.rhBM.price.tr,
  method = "nnet",
  tuneGrid = nnetGrid,
  trControl = ctrl,
  metric = "RMSE",
  linout=TRUE
)
nnetFit
nnet.logprice <- nnetFit$finalModel
# > nnet.logprice
#
# a 16-10-1 network with 181 weights
# inputs: Barcelona categ.distr type.chalet type.duplex type.penthouse type.studio floor 
# hasLift floorLift log.size exterior rooms bathrooms hasParkingSpace ParkingInPrice
# log_activation 
#
# output(s): log.price 
#
# options were - linear output units  decay=0.5
#
}else{
  # we already know that the optimal parameters are size=10, decay=0.5
  set.seed(123)
  nnet.logprice <- nnet(log.price~., data=scaled.rhBM.price.tr, 
                size=10, decay=0.5, linout=TRUE, maxit=100)
}
```

```{r}
1-(mean(nnet.logprice$residuals^2)/var(scaled.rhBM.price.tr$log.price))
# [1] 0.8009131 # July, 2021 laptop
# [1] 0.7912618 # July, 2019, and January 2020!!!
# [1] 0.8002104 # September 17, 2019, 
``` 

```{r}
cor(rhBM.price$log.price[Itr],nnet.logprice$fitted.values)^2
#           [,1]
# [1,] 0.8002232 # September 17, 2019
# [1,] 0.7913048 # January 2020
# [1,] 0.8009471 # July, 2021 laptop
plot(rhBM.price$log.price[Itr],nnet.logprice$fitted.values,
     main=paste("Corr^2=",round(cor(rhBM.price$log.price[Itr],nnet.logprice$fitted.values)^2,2)))
```


```{r}
# Predicting in the test sample
y.hat.te.nn <- y.hat.te <- as.numeric( predict(nnet.logprice, newdata = scaled.rhBM.price.te) )
1-mean((scaled.rhBM.price.te$log.price-y.hat.te)^2)/var(scaled.rhBM.price.te$log.price)
# [1] 0.7920497 # January 2020
# [1] 0.7885274 # July 2021, laptop
cor(rhBM.price$log.price[Ite],y.hat.te)^2
# [1] 0.7892885 # September 17, 2019
# [1] 0.7929101 # January 2020
# [1] 0.7885802 # July 2021, laptop
plot(rhBM.price$log.price[Ite],y.hat.te,
     main=paste("Corr^2=",round(cor(rhBM.price$log.price[Ite],y.hat.te)^2,2)))
```

### Variable relevance measures

```{r}
library(mgcv)
library(ggplot2)
library(grid)
library(maptools)# For pointLabel

source("../../R_scripts/relev.ghost.var.R")
source("../../R_scripts/relev.rand.perm.R")
```

## Variable relevance matrix by ghost variables

```{r, fig.height=14, fig.width=14}
relev.ghost.out <- relev.ghost.var(model=nnet.logprice, 
                             newdata = scaled.rhBM.price.te,
                             func.model.ghost.var= lm)
```


```{r, fig.height=14, fig.width=14}
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.ghost.var(relev.ghost.out, n1=n.tr,
                     # resid.var=mean(nnet.logprice$residuals^2),
                                 vars=1:10, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
```

```{r final.graf.Gh.pdf, eval=FALSE}
if (printing) pdf(file="newVarRlevIdealista_nn_Gh.pdf", height=20, width=12)
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, 
                     # resid.var=mean(nnet.logprice$residuals^2),
                                 vars=1:10, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
if (printing) dev.off()
```

```{r final.graf.Gh.pdf.slides_1, eval=FALSE}
if (printing) pdf(file="newVarRlevIdealista_nn_Gh_3_3.pdf", height=16, width=12)
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, resid.var=mean(nnet.logprice$residuals^2),
                                 vars=1:9, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
if (printing) dev.off()
```

```{r final.graf.Gh.pdf.slides_2, eval=FALSE}
if (printing) pdf(file="newVarRlevIdealista_nn_Gh_2_5.pdf", height=12, width=20)
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, resid.var=mean(nnet.logprice$residuals^2),
                                 vars=1:10, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=5)
if (printing) dev.off()
```

```{r final.graf.Gh.pdf.slides_3, eval=FALSE}
if (printing) pdf(file="newVarRlevIdealista_nn_Gh_2_4.pdf", height=12, width=16)
plot.relev.ghost.var(relev.ghost.out, n1=n.tr, resid.var=mean(nnet.logprice$residuals^2),
                                 vars=1:8, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
if (printing) dev.off()
```
## Variable relevance matrix by random permutation

```{r}
relev.rand.out <- relev.rand.perm(model=nnet.logprice, 
                              newdata = rhBM.price[Ite,])
```


```{r, fig.height=14, fig.width=14}
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:16, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
```


```{r final.graf.RP.pdf, eval=FALSE}
if (printing) pdf(file="newVarRlevIdealista_nn_RP.pdf", height=20, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:12, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
if (printing) dev.off()
```

```{r final.graf.RP.pdf.slides_1, eval=FALSE}
if (printing) pdf(file="newVarRlevIdealista_nn_RP_3_3.pdf", height=16, width=12)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:9, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=3)
if (printing) dev.off()
```

```{r final.graf.RP.pdf.slides_2, eval=FALSE}
if (printing) pdf(file="newVarRlevIdealista_nn_RP_2_5.pdf", height=12, width=20)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:10, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=5)
if (printing) dev.off()
```

```{r final.graf.RP.pdf.slides_3, eval=FALSE}
if (printing) pdf(file="newVarRlevIdealista_nn_RP_2_4.pdf", height=12, width=16)
# Plotting only eigenvectors with more than 1% of total relevance
plot.relev.rand.perm(relev.rand.out, relev.ghost=relev.ghost.out$relev.ghost,
                                 vars=1:8, sum.lm.tr=NULL,
                                 alpha=.01, ncols.plot=4)
if (printing) dev.off()
```

***Addendum after having sent the paper to publish***
<!--- 2019
When computing relevances by Ghost variables, the most relevant variable is `log.size`, while by random permutations those marked as most relevant are `floor` and  `bathrooms`.

We will remove those variables (one at a time) from the set of explanatory variables and then train again the neural network. We will compare the reduction in $R^2$ corresponding to each removed variable. The most important variable is that with a larger reduction. Will it be that indicated by ghost variables, or those indicated by random permutations?
-->

<!-- 2020 
When computing relevances by Ghost variables, the most relevant variable is `log.size`, while by random permutations those marked as most relevant are `type.penthouse`, `floor` and  `bathrooms`.

In order to compute the relevance by omission of those variables, we remove them (one at a time) from the set of explanatory variables and then train again the neural network. 
The most important variable is that with a larger relevance by omission. 
Will it be that indicated by ghost variables, or those indicated by random permutations?
-->

<!-- 2021 -->
When computing relevances by Ghost variables, the most relevant variable is `log.size`, while by random permutations those marked as most relevant are `rooms`, `floor` and  `categ.distr`.

In order to compute the relevance by omission of those variables, we remove them (one at a time) from the set of explanatory variables and then train again the neural network. 
The most important variable is that with a larger relevance by omission. 
Will it be that indicated by ghost variables, or those indicated by random permutations?


```{r}
names(scaled.rhBM.price.tr)
# [1] "price"           "Barcelona"       "categ.distr"    
# [4] "type.chalet"     "type.duplex"     "type.penthouse" 
# [7] "type.studio"     "floor"           "hasLift"        
#[10] "floorLift"       "log.size"        "exterior"       
#[13] "rooms"           "bathrooms"       "hasParkingSpace"
#[16] "ParkingInPrice"  "log_activation" 

relev.by.omission <- numeric(5) 
list.omission <- list(11,13,8,3,c(13,8,3))
```

**Removing `log.size`** 

```{r, results='hide'}
first.time.11 <- TRUE

if (first.time.11){
# tuning parameters "size" and "decay" using caret
require(caret)
ctrl <- trainControl(
  # method = "repeatedcv", # k-fold CV, k=num, repeated repeats times
  # repeats = 3, # number of repetitions of the k-fold CV
  method = "cv", # k-fold CV, k=num
  num=10 # default
)
nnetGrid = expand.grid(size = c(10,15,20), decay = c(0,.1,.3,.5))
set.seed(123)
nnetFit.11 <- train(
  log.price~., 
  data=scaled.rhBM.price.tr[,-11],
  method = "nnet",
  tuneGrid = nnetGrid,
  trControl = ctrl,
  metric = "RMSE",
  linout=TRUE
)
nnetFit.11
nnet.logprice.11 <- nnetFit.11$finalModel
# > nnet.logprice.11
#
# a 15-20-1 network with 171 weights
# inputs: Barcelona categ.distr type.chalet type.duplex type.penthouse type.studio floor hasLift floorLift exterior rooms bathrooms hasParkingSpace ParkingInPrice log_activation 
# output(s): .outcome 
# options were - linear output units  decay=0.5
#
}else{
  # we already know that the optimal parameters are size=20, decay=0.5
  set.seed(123)
  nnet.logprice.11 <- nnet(log.price~.,
                        data=scaled.rhBM.price.tr[,-11], 
                size=20, decay=0.5, linout=TRUE, maxit=100)
}

1-(mean(nnet.logprice.11$residuals^2)/var(scaled.rhBM.price.tr$log.price))
# [1] 0.7188321
# [1] 0.7095302 # Enero 2020
# [1] 0.7247141 # July 2021 laptop

cor(rhBM.price$log.price[Itr],nnet.logprice.11$fitted.values)^2
#           [,1]
# [1,] 0.7188247
#           [,1]
# [1,] 0.7095598 # Enero 2020
#          [,1]
# [1,] 0.7246971 # July 2021 laptop


# Predicting in the test sample
y.hat.te.11 <- as.numeric( predict(nnet.logprice.11, newdata = scaled.rhBM.price.te[,-11]) )

1-mean((scaled.rhBM.price.te$log.price-y.hat.te.11)^2)/var(scaled.rhBM.price.te$log.price)
# [1] 0.7060598 # Enero 2020
# [1] 0.6999083 # July 2021 laptop

cor(rhBM.price$log.price[Ite],y.hat.te.11)^2
# [1] 0.6960432
# [1] 0.7060634 # Enero 2020
# [1] 0.7002432 # July 2021 laptop

relev.by.omission[1] <- mean((y.hat.te.11 - y.hat.te.nn)^2)
```

**Removing `rooms`** 

```{r, results='hide'}
first.time.13 <- TRUE

if (first.time.13){
# tuning parameters "size" and "decay" using caret
require(caret)
ctrl <- trainControl(
  # method = "repeatedcv", # k-fold CV, k=num, repeated repeats times
  # repeats = 3, # number of repetitions of the k-fold CV
  method = "cv", # k-fold CV, k=num
  num=10 # default
)
nnetGrid = expand.grid(size = c(10,15,20), decay = c(0,.1,.3,.5))
set.seed(123)
nnetFit.13 <- train(
  log.price~., 
  data=scaled.rhBM.price.tr[,-13],
  method = "nnet",
  tuneGrid = nnetGrid,
  trControl = ctrl,
  metric = "RMSE",
  linout=TRUE
)
nnetFit.13
nnet.logprice.13 <- nnetFit.13$finalModel
# > nnet.logprice.13
#
# a 15-20-1 network with 341 weights
# inputs: Barcelona categ.distr type.chalet type.duplex type.penthouse type.studio floor hasLift floorLift log.size exterior bathrooms hasParkingSpace ParkingInPrice log_activation 
# output(s): .outcome 
# options were - linear output units  decay=0.3
#
}else{
  # we already know that the optimal parameters are size=10, decay=0.3
  set.seed(123)
  nnet.logprice.13 <- nnet(log.price~.,
                        data=scaled.rhBM.price.tr[,-13], 
                size=20, decay=0.3, linout=TRUE, maxit=100)
}

1-(mean(nnet.logprice.13$residuals^2)/var(scaled.rhBM.price.tr$log.price))
# [1] 0.8007802

cor(rhBM.price$log.price[Itr],nnet.logprice.13$fitted.values)^2
#           [,1]
# [1,] 0.8007731

# Predicting in the test sample
y.hat.te.13 <- as.numeric( predict(nnet.logprice.13, newdata = scaled.rhBM.price.te[,-13]) )

1-mean((scaled.rhBM.price.te$log.price-y.hat.te.13)^2)/var(scaled.rhBM.price.te$log.price)
# [1] 0.7878334

cor(rhBM.price$log.price[Ite],y.hat.te.13)^2
# [1] 0.78791

relev.by.omission[2] <- mean((y.hat.te.13 - y.hat.te.nn)^2)
```

**Removing `floor`** 

```{r, results='hide'}
first.time.8 <- TRUE

if (first.time.8){
# tuning parameters "size" and "decay" using caret
require(caret)
ctrl <- trainControl(
  # method = "repeatedcv", # k-fold CV, k=num, repeated repeats times
  # repeats = 3, # number of repetitions of the k-fold CV
  method = "cv", # k-fold CV, k=num
  num=10 # default
)
nnetGrid = expand.grid(size = c(10,15,20), decay = c(0,.1,.3,.5))
set.seed(123)
nnetFit.8 <- train(
  log.price~., 
  data=scaled.rhBM.price.tr[,-8],
  method = "nnet",
  tuneGrid = nnetGrid,
  trControl = ctrl,
  metric = "RMSE",
  linout=TRUE
)
nnetFit.8
nnet.logprice.8 <- nnetFit.8$finalModel
# > nnet.logprice.8
#
# a 15-20-1 network with 341 weights
# inputs: Barcelona categ.distr type.chalet type.duplex type.penthouse type.studio hasLift floorLift log.size exterior rooms bathrooms hasParkingSpace ParkingInPrice log_activation 
# output(s): .outcome 
# options were - linear output units  decay=0.5
#
}else{
  # we already know that the optimal parameters are size=10, decay=0.3
  set.seed(123)
  nnet.logprice.8 <- nnet(log.price~.,
                        data=scaled.rhBM.price.tr[,-8], 
                size=20, decay=0.5, linout=TRUE, maxit=100)
}

1-(mean(nnet.logprice.8$residuals^2)/var(scaled.rhBM.price.tr$log.price))
# 1] 0.8012655

cor(rhBM.price$log.price[Itr],nnet.logprice.8$fitted.values)^2
#           [,1]
# [1,] 0.8012655

# Predicting in the test sample
y.hat.te.8 <- as.numeric( predict(nnet.logprice.8, newdata = scaled.rhBM.price.te[,-8]) )

1-mean((scaled.rhBM.price.te$log.price-y.hat.te.8)^2)/var(scaled.rhBM.price.te$log.price)
# [1] 0.7856834

cor(rhBM.price$log.price[Ite],y.hat.te.8)^2
# [1] 0.7859383

relev.by.omission[3] <- mean((y.hat.te.8 - y.hat.te.nn)^2)
```


**Removing `catyeg.distr`** 


```{r, results='hide'}
first.time.3 <- TRUE

if (first.time.3){
# tuning parameters "size" and "decay" using caret
require(caret)
ctrl <- trainControl(
  # method = "repeatedcv", # k-fold CV, k=num, repeated repeats times
  # repeats = 3, # number of repetitions of the k-fold CV
  method = "cv", # k-fold CV, k=num
  num=10 # default
)
nnetGrid = expand.grid(size = c(10,15,20), decay = c(0,.1,.3,.5))
set.seed(123)
nnetFit.3 <- train(
  log.price~., 
  data=scaled.rhBM.price.tr[,-3],
  method = "nnet",
  tuneGrid = nnetGrid,
  trControl = ctrl,
  metric = "RMSE",
  linout=TRUE
)
nnetFit.3
nnet.logprice.3 <- nnetFit.3$finalModel
# > nnet.logprice.3
#
# a 15-20-1 network with 341 weights
# inputs: Barcelona type.chalet type.duplex type.penthouse type.studio floor hasLift floorLift log.size exterior rooms bathrooms hasParkingSpace ParkingInPrice log_activation 
# output(s): .outcome 
# options were - linear output units  decay=0.5
#
}else{
  # we already know that the optimal parameters are size=10, decay=0.3
  set.seed(123)
  nnet.logprice.3 <- nnet(log.price~.,
                        data=scaled.rhBM.price.tr[,-3], 
                size=20, decay=0.5, linout=TRUE, maxit=100)
}

1-(mean(nnet.logprice.3$residuals^2)/var(scaled.rhBM.price.tr$log.price))
# [1] 0.7831749

cor(rhBM.price$log.price[Itr],nnet.logprice.3$fitted.values)^2
#           [,1]
# [1,] 0.7831991

# Predicting in the test sample
y.hat.te.3 <- as.numeric( predict(nnet.logprice.3, newdata = scaled.rhBM.price.te[,-3]) )

1-mean((scaled.rhBM.price.te$log.price-y.hat.te.3)^2)/var(scaled.rhBM.price.te$log.price)
# [1] 0.7634722

cor(rhBM.price$log.price[Ite],y.hat.te.3)^2
# [1] 0.7635141

relev.by.omission[4] <- mean((y.hat.te.3 - y.hat.te.nn)^2)
```



**Removing `penthouse`, `floor` and `bathrooms`** 


```{r, results='hide'}
first.time.13.8.3 <- TRUE

if (first.time.13.8.3){
# tuning parameters "size" and "decay" using caret
require(caret)
ctrl <- trainControl(
  # method = "repeatedcv", # k-fold CV, k=num, repeated repeats times
  # repeats = 3, # number of repetitions of the k-fold CV
  method = "cv", # k-fold CV, k=num
  num=10 # default
)
nnetGrid = expand.grid(size = c(10,15,20), decay = c(0,.1,.3,.5))
set.seed(123)
nnetFit.13.8.3 <- train(
  log.price~., 
  data=scaled.rhBM.price.tr[,-c(13,8,3)],
  method = "nnet",
  tuneGrid = nnetGrid,
  trControl = ctrl,
  metric = "RMSE",
  linout=TRUE
)
nnetFit.13.8.3
nnet.logprice.13.8.3 <- nnetFit.13.8.3$finalModel
# > nnet.logprice.13.8.3
#
# a 13-20-1 network with 301 weights
# inputs: Barcelona type.chalet type.duplex type.penthouse type.studio hasLift floorLift log.size exterior bathrooms hasParkingSpace ParkingInPrice log_activation 
# output(s): .outcome 
# options were - linear output units  decay=0.3
#
}else{
  # we already know that the optimal parameters are size=10, decay=0.3
  set.seed(123)
  nnet.logprice.13.8.3 <- nnet(log.price~.,
                        data=scaled.rhBM.price.tr[,-c(13,8,3)], 
                size=20, decay=0.3, linout=TRUE, maxit=100)
}

1-(mean(nnet.logprice.13.8.3$residuals^2)/var(scaled.rhBM.price.tr$log.price))
# [1] 0.7586767

cor(rhBM.price$log.price[Itr],nnet.logprice.13.8.3$fitted.values)^2
#         [,1]
# [1,] 0.75868

# Predicting in the test sample
y.hat.te.13.8.3 <- as.numeric( predict(nnet.logprice.13.8.3, newdata = scaled.rhBM.price.te[,-c(13,8,3)]) )

1-mean((scaled.rhBM.price.te$log.price-y.hat.te.13.8.3)^2)/var(scaled.rhBM.price.te$log.price)
# [1] 0.7388711

cor(rhBM.price$log.price[Ite],y.hat.te.13.8.3)^2
# [1] 0.7391262

relev.by.omission[5] <- mean((y.hat.te.13.8.3 - y.hat.te.nn)^2)
```

```{r}
MSPE.tr <- mean(nnet.logprice$residuals^2)
MSPE.te <- mean((scaled.rhBM.price.te$log.price-y.hat.te)^2)
(relev.by.omission <- relev.by.omission/MSPE.te)
# [1] 2.3351372 0.4199004 0.4806855 1.0032761 1.3221101
```